---
title: "p8105_hw1_md4036"
author: "Margaret"
date: "2022-09-22"
output: github_document
---

We are first going to download the tidyverse library.

```{r loading tidyverse package}
library(tidyverse)
```


# Problem 1

We are downloading and displaying the "Penguins" dataset here.

```{r loading penguins package}
data("penguins", package = "palmerpenguins")
head(penguins)
```

### Description of the "Penguins" dataset:

The "Penguins" dataset consists of 8 variables including species, island, bill length, bill depth, flipper length, body mass, sex, and year. This dataset has `r ncol(penguins)` columns and `r nrow(penguins)` rows. 

The mean bill length is `r round(mean(pull(penguins, bill_length_mm), na.rm = TRUE))`mm.

The mean bill depth is `r round(mean(pull(penguins, bill_depth_mm), na.rm = TRUE))`mm.

The mean body mass is `r round(mean(pull(penguins,body_mass_g), na.rm = TRUE))`g.

The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE))` mm.


## The Mean Flipper Length

The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE))` mm.

## Scatterplot with flipper length and bill length

```{r loading ggplot2 package}
library(ggplot2)
```

```{r scatterplot with bill length and flipper length}
ggplot (penguins, aes (x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() 

ggsave ("scatter_plot.pdf")
```


# Problem 2

```{r homework1 dataframe creation}
homework1_df = 
  tibble (
    random_sample = rnorm (10),
    vec_logic = random_sample > 0,
    vec_char = c ("a","b","c","d","e","f","g","h","i","j"),
    vec_factor = factor(c("low","medium","low","high","low","high","medium","low","low","high"))
  )

homework1_df
```

"random_sample" mean is `r mean(pull(homework1_df, random_sample))`. 

"vec_logic" mean is `r mean(pull(homework1_df, vec_logic))`.

"vec_char" mean is `r mean(pull(homework1_df, vec_char))`.

"vec_factor" mean is `r mean(pull(homework1_df, vec_factor))`.

Since both of the "vec_char" and the "vec_factor" variables do not consist of numeric values, they do not have mean values. 

```{r coververting variable types with as.numeric,results="hide"}
as.numeric (homework1_df$vec_logic)

as.numeric (factor(homework1_df$vec_char))

as.numeric (homework1_df$vec_factor)
```









